Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2025-01-31 ms-3/ms.tex
Update ms.tex

The next paragraph should look across all counties and reference Fig 3.

>>>>

Highly overdispersed patterns were observed for many of the examined counties more frequently later in time series, consistent with more heterogeneity in transmission, susceptibility and reporting. 
In addition, there are increases in dispersion around the peaks in incidence (Figure~\ref{fig3}).
Evidence for a change in \begin{math}\theta\end{math} was observed across many counties (evidenced by a concentration of low p-values around peak incidence) (Fig\ 3 f). Note that these p-values should be corrected for multiple testing when used for inference instead of visualization.
Raising variance relative to mean (higher dispersion) implies spatiotemporal "crowding" of cases (i.e. localized surges) which may necessitate more surge capacity in hospitals and testing centers. 
It appears that there are more surges on the way up to, and on the way down from, peak incidence, some of which departs from the dispersion expected under standard epidemic theory. 
This indicates less diffuse epidemic dynamics that are potentially more subject to climate forcing \cite{dalziel_urbanization_2018}, and increased locally experienced mean density \cite{lloyd_mean_1967} at unexpected points in the COVID-19 pandemic.
